---
title: "Assigment"
author: "A"
date: "2024-09-12"
output: html_document
---

```{r}
library("tidyverse")

```

```{r}
superm <- read.csv(file.choose())
```

```{r}
str(superm)
```
```{r}
view(superm)
```

###show the total number of rows and column on the supermarket dataset.questn 1
```{r}
dim(superm)
```
##show 
```{r}
superm%>%
 filter(Units.Sold =="5")%>%
   group_by(Product.Family)%>%
  summarise(customer.purchase_count=n())
```
##show the Total revenue realised in the supermarket.questn3
```{r}
superm%>%
  summarise(Total_Revenue=sum(Revenue))
```
##show the total count of sales alloted on each  items in the ##Product.category.questn4
```{r}
superm%>%
  group_by(Product.Category)%>%
  summarise(Total_Revenue=n())
```
 ##show the items in dataset that had the highest sales by revenue on product.category in the ##supermarket.questn5
 
```{r}
superm%>%
  group_by(Product.Category,Revenue)%>%
  summarise(Total_count=n())%>%
  head(1)
```
 ##show the top 2 most purchased items in product family.questn6
```{r}
superm%>%
  group_by(Product.Family)%>%
  summarise(sales_count=n())%>%
  arrange(desc(sales_count))%>%
  head(2)
  
```
 ##show the top 2 most purchased items in product.Department.questn7
```{r}
superm%>%
  group_by(Product.Department)%>%
  summarise(sales_count=n())%>%
  arrange(desc(sales_count))%>%
  head(2)
```
##show the top 2 most purchased items in product.Category.questn8
```{r}
superm%>%
  group_by(Product.Category)%>%
  summarise(sales_count=n())%>%
  arrange(desc(sales_count))%>%
  head(2)
```
##show the total count of sales alloted on different  items in the Product.Departmet.questn9
```{r}
superm%>%
  group_by(Product.Department)%>%
   summarise(Sales_count=n())
 
```
##show the items in dataset that had the highest sales by revenue on product.Department in the ##supermarket.quest10
```{r}
superm%>%
  group_by(Product.Department,Revenue)%>%
  summarise(Total_count=n())%>%
  head(1)
```
#show the total count of customer that had purchased of more than 5 units in the supermarket
```{r}
superm%>%
  filter(Units.Sold>"5")%>%
  
  summarise(customer_count=n())
```
##show the total count of married  who are home  owners by country that did shopping from the supermarket questn 12
```{r}
superm%>%
  filter(Marital.Status=="M" & Homeowner=="Y")%>%
  group_by(Country,Marital.Status,Gender,Homeowner)%>%
summarise(count=n())
  
  
```
show total count of only married female that are home owners questn 13
```{r}
superm%>%
  filter(Marital.Status=="M" & Gender=="F" & Homeowner=="Y")%>%
  group_by(Country,Marital.Status,Gender,Homeowner)%>%
summarise(count=n())
```
show that of only male gender..questn 14
```{r}
superm%>%
  filter(Marital.Status=="M" & Gender=="M" & Homeowner=="Y")%>%
  group_by(Country,Marital.Status,Gender,Homeowner)%>%
summarise(count=n())
```
##show married couple with more than 2children based on countrt quetsn15
```{r}
superm%>%
  filter(Marital.Status=="M" & Children>"4" & Gender %in% c("M","F"))%>%
  group_by(Annual.Income,Marital.Status,Gender)%>%
summarise(count=n())
```
#show the average unit sold of each items of the Product.category on a column Chat. questn16
```{r}
superm%>%
  group_by(Product.Category)%>%
  summarise(avg_Units.Sold_Product.Category=round(mean(Units.Sold),2)) %>%
  arrange(desc(avg_Units.Sold_Product.Category))%>%
  ggplot(aes(x =reorder(Product.Category,avg_Units.Sold_Product.Category),
  y=avg_Units.Sold_Product.Category,fill=Product.Category))+
  geom_col()+
  coord_flip()+
  ylab("avg_Units.Sold_Product.Category")
 xlab("Product.Category")

  
  

  
  
```
show the revenue generated on each items of the product.fmaily on a column chart /questn17
```{r}
superm%>%
  group_by(Product.Family)%>%
  summarise(total_Revenue=sum(Revenue))%>%
 arrange(desc(total_Revenue))%>%
  ggplot(aes(x =reorder(Product.Family,total_Revenue),
  y=total_Revenue,fill=Product.Family))+
  geom_col()+
  coord_flip()+
  ylab("total revenue on each Product.Family")
xlab("Product.Family")
```
##show a chat of the revenue generated in each city  using geom jitter .questn 18
```{r}
superm%>%
  group_by(City)%>%
  summarise(yearly_Revenue=sum(Revenue))%>%
  arrange(desc(yearly_Revenue))%>%
  ggplot(aes(x=City, y=yearly_Revenue))+
  geom_jitter()
```
##show a chat of the revenue generated from the male and female customers in the supermaker using Geom_box plot chat questn 19
```{r}
superm%>%
  
  group_by(Gender)%>%
  summarise(yearly_Revenue=sum(Revenue))%>%
  ggplot(aes(x=Gender, y=yearly_Revenue))+
  geom_boxplot()
```
##show a chat bwteen home owners and that of Non Homeowners by their yearly revenue questn 20
```{r}
superm%>%
  group_by(Homeowner)%>%
  summarise(total_Revenue=sum(Revenue))%>%
  arrange(desc(total_Revenue))%>%
  ggplot(aes(x=reorder(Homeowner,total_Revenue),
  y=total_Revenue,fill=Homeowner))+
  geom_col()+
  coord_flip()+
  ylab("total revenue on both Home & non Homeowners")
xlab("Homeowners")
              
  
```
##give a chat that shows yearly revenue between Home owners and those who are non-Homeowners

```{r}
